Stream of Consciousness Literature: A 'Joyceless' Linguistic Landscape

### 2024-04-25 paper/paper.qmd
final paper updates

The findings in this paper reveals a correlative relationship between SOC literature and mental health-inclined vocabulary and linguistic patterns. In terms of frequency, a dominant portion-or over 60% of words in the NRC index-of select SOC texts in this analysis have negative and sadness-leaning words ([@fig-sentiment-frequency]) ([@fig-sentiment-category]) ([@fig-sentiment-number]). Most repeated words are abstract, temporal nouns like \textit{time}, \textit{mind} or \textit{life}, which are aligned with SOC literature's exploration of mind wandering, non-linearity and unconscious cognition ([@fig-word-networks]).

>>>>

The findings in this paper reveals a correlative relationship between SOC literature and mental health-inclined vocabulary and linguistic patterns. In terms of frequency, a dominant portion-over 60% of words in the NRC index-from select SOC texts have negative and sadness-leaning words ([@fig-sentiment-frequency]) ([@fig-sentiment-category]) ([@fig-sentiment-number]). Most repeated words are abstract, temporal nouns like \textit{time}, \textit{mind} or \textit{life}, which are aligned with SOC literature's exploration of mind wandering, non-linearity and unconscious cognition ([@fig-word-networks]).
